SDR enhancement by clouds

### 2024-03-13 article/article.Rmd
Commit 2024-03-13 12:10

$\text{GHI}_\text{CSi}$: modelled clear sky one minute global horizontal irradiance

$\text{GHI}_\text{CSi}$: modelled clear sky one minute global horizontal irradiance

@@

Furthermore, to account for the Sun's variability in our one-minute GHI measurements, we adjusted the model's input spectrum integral to the one of the the TSI provided by NOAA.
Finally, we adjusted for the effect of Sun - Earth distance, and calculated the clear sky irradiance value at the horizontal plane by using the cosine of the corresponding interpolated SZA. 
For each period of the year, we used the appropriate atmospheric profile (afglms or afglmw).
Thus, the modeled GHI_modeld we can directly compare each measured one minute value of GHI, with the expected clear sky radiation.

@@

@@

 We applied the effect of

>>>>

$\text{GHI}_\text{mCSi}$: modelled clear sky one minute global horizontal irradiance

@@

Furthermore, to account for the Sun's variability in our one-minute GHI measurements, we adjusted the model's input spectrum integral to the one of the the TSI provided by NOAA.
Finally, we adjusted for the effect of the Sun - Earth distance, and calculated the clear sky irradiance value at the horizontal plane by using the cosine of the corresponding interpolated SZA. 
For each period of the year, we used the appropriate atmospheric profile (afglms or afglmw).
Thus, the modelled GHI_modeld we can directly compare each measured one minute value of GHI, with the expected clear sky radiation.

@@

Of course, have to choose which atmospheric conditions qualify as a good clear sky analogous radiation.

@@

Which is an expected result as these values represent an typical atmosphere in Thessaloniki with low load of aerosols and humidity, which are the main factor that atternuate the GHI, execluding clouds.
